Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-16 pedestrian_forecasting_iros_2017.tex
added one detail to Ram's ammendment

This is a powerful result since it allows us to compute $\Pr( x_t, \hat{x}_0, \hat{v}_0)$  (and thus $\rho_t(x_t)$) at times $t \in \{\Delta t, \dots, N_t \Delta t\}$ with a single computation of $\Phi_{k,1}^{\ell \Delta t \bar{s}}( x_0^{i,j})$ for each $\ell \in  \{-N_t,\dots,N_t\}$, $k \in \{1,\dots,n\}$, and $x_0^{i,j} \in \Gamma_L( \hat{x}_0 , N_x)$.
To appreciate this, assume we are given $\Phi_{k,1}^{m  \bar{s} \Delta t}(x_0^{i,j})$ for all $m \in \{ -\ell, \ldots, \ell \}$.
We can then use the regular partition
\begin{align}
	\mathcal{P}_\ell := \left\{ \frac{m}{\ell} \bar{s} \right\}_{m=-\ell}^{\ell} \label{eq:partition}
\end{align}
of $[-\bar{s}, \bar{s}]$ to compute a Riemann sum approximation using Theorem \ref{thm:main}.
The partition $\mathcal{P}_\ell$ has a width of size, $\Delta s = \bar{s} / \ell$, and substitution in \eqref{eq:approximation 3} yields an approximation of $\Pr( x_t, \hat{x}_0, \hat{v}_0)$ at time $t=\ell \Delta t$
given by
\begin{align*}
	\begin{split}
		&\frac{\bar{s}}{\ell} \sum_{i,j,k,m} W(k,m \bar{s} / \ell ,i,j,\hat{x}_0) \left. \Pr( x_t \mid \check{x}_t ) \right|_{ \check{x}_t = \Phi_{k,1}^{m \bar{s} \Delta t}( x_0^{i,j}) } \\
		&\qquad+\Pr( x_t , lin, \hat{x}_0, \hat{v}_0 ).
	\end{split}
\end{align*}
As we have already computed $\Phi_{k,1}^{m \bar{s} \Delta t}$ for $| m | \leq \ell$ by assumption, the only obstacle to computing this sum is the computation of the weights $W(k,m \bar{s} / \ell ,i,j,\hat{x}_0)$.
Now if we want to compute $\Pr( x_t, \hat{x}_0, \hat{v}_0)$ at $t=(\ell + 1 ) \Delta t$, then by reusing the earlier computation one would only need to compute $\Phi_{k,1}^{m  \bar{s} \Delta t}(x_0^{i,j})$ for $m \in \{ -( \ell + 1 ), (\ell + 1 )\}$ along with the weights.
%Admittedly, this means our approximations might be imprecise over very short times, but more accurate over longer time-horizons.

>>>>

This is a powerful result since it allows us to compute $\Pr( x_t, \hat{x}_0, \hat{v}_0)$  (and thus $\rho_t(x_t)$) at times $t \in \{\Delta t, \dots, N_t \Delta t\}$ with a single computation of $\Phi_{k,1}^{\ell \Delta t \bar{s}}( x_0^{i,j})$ for each $\ell \in  \{-N_t,\dots,N_t\}$, $k \in \{1,\dots,n\}$, and $x_0^{i,j} \in \Gamma_L( \hat{x}_0 , N_x)$.
To appreciate this, assume we are given $\Phi_{k,1}^{m  \bar{s} \Delta t}(x_0^{i,j})$ for all $m \in \{ -\ell, \ldots, \ell \}$.
We can then use the regular partition
\begin{align}
	\mathcal{P}_\ell := \left\{ \frac{m}{\ell} \bar{s} \right\}_{m=-\ell}^{\ell} \label{eq:partition}
\end{align}
of $[-\bar{s}, \bar{s}]$ to compute a Riemann sum approximation using Theorem \ref{thm:main}.
The partition $\mathcal{P}_\ell$ has a width of size, $\Delta s = \bar{s} / \ell$, and substitution in \eqref{eq:approximation 3} yields an approximation of $\Pr( x_t, \hat{x}_0, \hat{v}_0)$ at time $t=\ell \Delta t$
given by
\begin{align*}
	\begin{split}
		&\frac{\bar{s}}{\ell} \sum_{i,j,k,m} W(k,m \bar{s} / \ell ,i,j,\hat{x}_0) \left. \Pr( x_t \mid \check{x}_t ) \right|_{ \check{x}_t = \Phi_{k,1}^{m \bar{s} \Delta t}( x_0^{i,j}) } \\
		&\qquad+\Pr( x_t , lin, \hat{x}_0, \hat{v}_0 ).
	\end{split}
\end{align*}
As we have already computed $\Phi_{k,1}^{m \bar{s} \Delta t}$ for $| m | \leq \ell$ by assumption, the only obstacle to computing this sum is the computation of the weights $W(k,m \bar{s} / \ell ,i,j,\hat{x}_0)$.
Now if we want to compute $\Pr( x_t, \hat{x}_0, \hat{v}_0)$ at $t=(\ell + 1 ) \Delta t$, then by reusing the earlier computation one would only need to compute $\Phi_{k,1}^{m  \bar{s} \Delta t}(x_0^{i,j})$ for $m \in \{ -( \ell + 1 ), (\ell + 1 )\}$ along with the weights to obtain an approximation using the partition $\mathcal{P}_{\ell + 1}$.
%Admittedly, this means our approximations might be imprecise over very short times, but more accurate over longer time-horizons.
